Compact Core Galaxies in the RESOLVE Survey

### 2016-04-18 paperdraft.tex
more changes

For both the one and two component fits, \textsc{Galfit} outputs a text file with the best fits for central x \& y position of the model, integrated magnitude, \Reff, S\'ersic n, axial ratio (b/a), and position angle and a $\chi^2/\nu$ as well as a fits file that contains the data, best fit model, and residual images.

@@

We start our search for CCGs by using the one component fit from the above analysis and select galaxies with \Reff\ values $<1000$ pc. Since we are looking for galaxies with compact cores, going up to \Reff\ $\sim 1000$ pc allows us to select objects with cores that are dominating the light and therefore may have a smaller core \Reff\ in a two component fit. We also limit the  $\chi^2/\nu$ to be $<1.3$, since values above this represent galaxies with large residuals left over, which are spirals or irregulars that we would not consider ``cored". After this selection, we are left with 124 galaxies in the CCG candidate sample.

@@

We quantify the amount of light in the core vs. the envelope by taking a ratio of the fluxes of the core and the envelope. The flux of each component is computed with $m = -2.5 \times \log({\rm flux})$, where $m$ is the integrated magnitude output from \textsc{Galfit}. For each plot in this paper, we color code the CCGs by the logarithm of the flux ratio. CCGs with more light in the envelope will have log(flux ratio) $<$ 0, and will hereafter be called ``envelope-dominated' CCGs. CCGs with more light in the core will have log(flux ratio) $>$ 0, and will hereafter be called ``core-dominated'' CCGs. CCGs with log(flux ratio) $\sim 0$ will have both a bright core plus an extended envelope, and will be called ``core+envelope'' CCGs. See \autoref{fig:pics} for examples of CCGs on this scale. There are some cases when \textsc{Galfit} cannot find a core or an envelope, and will instead fit an extremely large and faint component instead. Where this happens (5 out of 96 cases), we classify this fit as either all core/envelope depending on which component was bad (log(flux ratio) = -1 or 1). We also see in 4 out of the 96 cases that the \Reff\ values for each component will be exactly the same value to 3-4 decimal points, indicating a probable bad fit for one component. When this occurs, we classify the galaxy as being all core (log(flux ratio) = 1).

@@

\subsection{Photometry: galaxy colors, stellar and baryonic masses, and star formation rates}
\label{phot}
\noindent The RESOLVE survey overlaps with a number of photometric surveys, including GALEX $NUV$ \citep{Morrissey2007}, SDSS-DR8 $ugriz$ \citep{Aihara2011}, and UKIDSS $YHK$ and/or 2MASS $JHK$ \citep{Skrutskie2006}. We reprocess this photometric data to improve upon the standard SDSS data pipeline, as described in \citet{Eckert2015}. The main differences in this processing are (1) improved sky subtraction following Blanton et al. (2011) for SDSS photometry plus custom background subtraction for UKIDSS/2MASS, (2) the definition of elliptical apertures on the sum of the higher S/N $gri$ images to determine the PA and b/a ratio of the outer disk (if present), and (3) the application of the same apertures to all bands which allows us to measure magnitudes for galaxies that may not have been detected by automated survey pipelines, especially low surface brightness galaxies in 2MASS, UKIDSS, and GALEX. Then, total magnitudes are derived for each band using an exponential outer disk fit method, curve of growth method, or color correction method (see Figure 2 in \citet{Eckert2015}).

@@

\noindent A subset of the smallest galaxies in RESOLVE are observed with the Gemini-South IFU for their kinematics instead of SOAR. For this absorption-line setup, we use the B1200 grating in 1-slit mode to cover a spatial region of 3"$\times$5" and the spectral range 4200-5600\AA. The B1200 grating offers 0.9\AA\ resolution when binned spectrally by 2. We calculate our exposure times such that we achieve S/N $\sim$ 25 per \AA\, after binning by 2 in the spectral direction and summing the fibers out to \Reff.

The spectral reduction proceeds as follows. Using the standard IRAF Gemini-GMOS data packages, bias and overscan subtraction, spatial trimming, flat fielding and fiber identification are performed. We next use the GMOS package gemCRspec, a wrapper for \texttt{LA\_COSMIC}, to clean cosmic rays from each science exposure. We then correct the science frames for quantum efficiency differences between CCDs. Wavelength transformation, sky subtraction, and flux calibration are subsequently performed, and lastly, data cubes are made and summed. We then stack the individual fiber spectra out to \Reff\ to create a 1D spectrum for each galaxy that has S/N $\sim25$. More information on the data reduction for the Gemini GMOS IFU can be found in  Appendix A.

@@

\appendix

>>>>

For both the one and two component fits, \textsc{Galfit} outputs a text file with the best fits for central x \& y position of the model, integrated magnitude, \Reff, S\'ersic n, axial ratio (b/a), and position angle and a $\chi^2/\nu$ as well as a fits file that contains the data, best fit model, and residual images. See \autoref{fig:galfit} for example one and two component fits for a RESOLVE galaxy.

\begin{figure*}[b]
\begin{center}
\includegraphics{galfitexample.eps}
\caption{}
\label{fig:galfit}
\end{center}
\end{figure*}

@@

We start our search for CCGs by using the one component fit from the above analysis and select galaxies with \Reff\ values $<1000$ pc. Since we are looking for galaxies with compact cores, going up to \Reff\ $\sim 1000$ pc allows us to select objects with cores that are dominating the light and therefore may have a smaller core \Reff\ in a two component fit. We also limit the  $\chi^2/\nu$ to be $<1.3$, since values above this represent galaxies with large residuals left over, which are normally spirals or irregulars that we would not consider a CCG. After this selection, we are left with 124 galaxies in the CCG candidate sample.

@@

We quantify the amount of light in the core vs. the envelope by taking a ratio of the fluxes of the core and the envelope. The flux of each component is computed with $m = -2.5 \times \log({\rm flux})$, where $m$ is the integrated magnitude output from \textsc{Galfit}. For each plot in this paper, we color code the CCGs by the logarithm of the flux ratio. CCGs with more light in the envelope will have log(flux ratio) $<$ 0, and will hereafter be called ``envelope-dominated' CCGs. CCGs with more light in the core will have log(flux ratio) $>$ 0, and will hereafter be called ``core-dominated'' CCGs. CCGs with log(flux ratio) $\sim 0$ will have both a bright core plus an extended envelope, and will be called ``core+envelope'' CCGs. See \autoref{fig:pics} for examples of CCGs on this continuous scale. There are some cases when \textsc{Galfit} cannot find a core or an envelope, and will instead fit an extremely large and faint component instead. Where this happens (5 out of 96 cases), we classify this fit as either all core/envelope depending on which component was bad (log(flux ratio) = -1 or 1). We also see in 4 out of the 96 cases that the \Reff\ values for each component will be exactly the same value to 3-4 decimal points, indicating a probable bad fit for one component. When this occurs, we classify the galaxy as being all core (log(flux ratio) = 1).

@@

\subsection{Photometry: galaxy colors, stellar and baryonic masses, and star formation rates}
\label{phot}
\noindent The RESOLVE survey overlaps with a number of photometric surveys, including GALEX $NUV$ \citep{Morrissey2007}, SDSS-DR8 $ugriz$ \citep{Aihara2011}, and UKIDSS $YHK$ and/or 2MASS $JHK$ \citep{Skrutskie2006}. We reprocess this photometric data to improve upon the standard SDSS data pipeline, as described in detail in \citet{Eckert2015}. The main differences in this processing are (1) improved sky subtraction following Blanton et al. (2011) for SDSS photometry plus custom background subtraction for UKIDSS/2MASS, (2) the definition of elliptical apertures on the sum of the higher S/N $gri$ images to determine the PA and b/a ratio of the outer disk (if present), and (3) the application of the same apertures to all bands which allows us to measure magnitudes for galaxies that may not have been detected by automated survey pipelines, especially low surface brightness galaxies in 2MASS, UKIDSS, and GALEX. Then, total magnitudes are derived for each band using an exponential outer disk fit method, curve of growth method, or color correction method (see Figure 2 in \citet{Eckert2015}).

@@

\noindent A subset of the faintest or smallest galaxies in RESOLVE are observed with the Gemini-South IFU for their kinematics instead of SOAR. For this absorption-line setup, we use the B1200 grating in 1-slit mode to cover a spatial region of $3''\times5''$ and the spectral range 4200-5600\AA. The B1200 grating offers 0.9\AA\ resolution when binned spectrally by 2. We calculate our exposure times such that we achieve S/N $\sim$ 25 per \AA\, after binning by 2 in the spectral direction and summing the fibers out to \Reff.

The spectral reduction proceeds as follows. Using the standard IRAF Gemini-GMOS data packages, bias and overscan subtraction, spatial trimming, flat fielding and fiber identification are performed. We next use the GMOS package gemCRspec, a wrapper for \texttt{LA\_COSMIC}, to clean cosmic rays from each science exposure. We then correct the science frames for quantum efficiency differences between CCDs. Wavelength transformation, sky subtraction, and flux calibration are subsequently performed, and lastly, data cubes are made and summed. We then stack the individual fiber spectra out to \Reff\ to create a 1D spectrum for each galaxy that has S/N $\sim25$. More information on the data reduction for the Gemini GMOS IFU can be found in \autoref{app}.

@@

\appendix
\label{app}
